Peer influences in air travel behavior: A social autoregressive analysis

### 2015-03-20 article.Rmd
Improved text in econometrics section.

For a linear regression model , a necessary assumption is that the observations
are independent, which is unlikely in spatial data. Tobler’s law implies that if
two observations are “close” to each other, then they are likely to share common
characteristics [@Tobler1970]. Further, observations close to each other may
actually exert an influence on each other in the way air pollution lowers the
price of nearby properties [@Kim2008]. If correlation and
interdependence are not controlled in an econometric model, then the model may
return biased parameters and/or invalid hypothesis tests.

@@

There are two primary difficulties in creating , one econometric and one
practical. From an econometric standpoint, the researcher typically must specify
exogenously. Though some common practices have emerged in the spatial literature
[@Dubin1998], not all of these can be readily adopted to social networks.
This gap in the literature is one that we seek to fill with this study, by
examining several possible  matrices that we construct from social network data.
The practical difficulty is actually collecting that data, though this is
becoming less difficult as interaction within social networks happens through
online sites such as Facebook. We discuss this practical evolution in Section
2.2.

@@

The online survey instrument was adapted from Wall et al (2014), and
contains three principal components.  For a detailed description of the
variables collected, refer to Wall et al. (2014).  The first component
collected respondents’ air travel information from the past year – this includes
a list of trips taken with origin and destination airports for round-trip,
multi-destination, and one-way travel.  The second component collected
socio-demographic information, including age, gender, income, education level,
citizenship, occupation, and race.  The third component asked respondents to log
in to their Facebook accounts, and the survey automatically collected data
contained in the respondent's profile and friends list via the Facebook
application programming interface (API).  This data included the hometown city
and current city locations of the respondents, and also that of the respondents’
friends.  The program also collected an encrypted (one way hash) version of the
Facebook ID for all respondents and their friends.  This ensured subject
anonymity while simultaneously allowing us to observe which
respondents were friends with each other, as well as how many friends respondents
have in common even if those common friends did not participate in the survey.

>>>>

For a linear regression model $y = X\beta + epsilon$, a necessary assumption is 
that the observations are independent, which is unlikely in spatial data. 
Tobler’s law suggests that if
two observations are “close” to each other, then they are likely to share common
characteristics [@Tobler1970]. Further, observations close to each other may
actually exert an influence on each other in the way air pollution lowers the
price of nearby properties [@Kim2008]. If correlation and
interdependence are not controlled in an econometric model, then the model may
return biased parameters and/or invalid hypothesis tests.

@@

There are two primary difficulties in creating $W$, one econometric and one
practical. From an econometric standpoint, the researcher typically must specify $W$
exogenously. Though some common practices have emerged in the spatial literature
[@Dubin1998], not all of these can be readily adopted to social networks.
This gap in the literature is one that we seek to fill with this study, by
examining several possible matrices that we construct from social network data.
The practical difficulty is actually collecting such data, though this is
becoming less difficult as interaction within social networks happens through
online sites such as Facebook. We discussed this practical evolution in Section
2.1.

@@

The online survey instrument was adapted from @Wall2014; a detailed description 
of the instrument can be found there. The survey consists of three principal 
components. The first component
collected respondents’ air travel information from the past year – this includes
a list of trips taken with origin and destination airports for round-trip,
multi-destination, and one-way travel.  The second component collected
socio-demographic information, including age, gender, income, education level,
citizenship, occupation, and race.  The third component asked respondents to log
in to their Facebook accounts, and the survey automatically collected data
contained in the respondent's profile and friends list via the Facebook
application programming interface (API).  This data included the hometown city
and current city locations of the respondents, and also that of the respondents’
friends.  The program also collected an encrypted (one way hash) version of the
Facebook ID for all respondents and their friends.  This ensured subject
anonymity while simultaneously allowing us to observe which
respondents were friends with each other, as well as how many friends respondents
have in common even if those common friends did not participate in the survey.
